\section{Ballroom}

\DndDropCapLine{T}{he Sensational Seven} were asked to leave all weapons at the door by the servant in order to join the ball. The team decided to persuade and hide their weapons from the servant, put on their masks, and enter the masquerade ball.



\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Selight of Hand  & 6 \\
	 & Persuasion  & 9 \\
	Ruben & Slight of Hand & 13 \\
	Xucphr & Persuasion  & 8\\
	 & Deception & 21 \\
\end{DndTable}
	

Xucphr goes to eat food at one of the tables. Ruben, Pyretrix, Gregory, go to another table to blend. Rayla walking around enjoying the festivities and music. Brolasi and Nova standing towards the entrance of the room but enjoying the party.

A Giff having a discussion about firearms with a noble lady but she appears to want their conversation to end.

As Ruben, Pyretrix, and Gregory are dancing at the dance floor, Xucphr started dancing as well as stuff his face with food. Xucphr started busting some shoulder moves and footwork which made everyone around him stare in amazement.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & Performance  & 18 \\
	Pyretrix & Performance & 13 \\
	Ruben & Performance (A) & 15 \\
\end{DndTable}

Pyretrix decided to check his surroundings to see if there's any conversations worth listening. 

\begin{DndComment}{Results}
Perception (13) - Notice the people around discussing about boring, rich people's conversation like economics. Nothing out of the ordinary; Very dull.
\end{DndComment}

\begin{DndTable}[color=PhbLightCyan]{cX}
	\textbf{Character} & \textbf{Perception Check (d20)}\\
	Xucphr & 19 \\
	Pyretrix & 5 \\
	Ruben (A) &  9 \\
	Rayla (A) & 16 \\
\end{DndTable}

\begin{DndComment}{Results}
Rayla - Notice the Count Aleksandr of Orlovski (Vampire Umbral Lord), Countess Katerina Orlovski (Drown Matron Mother), and a Vampire Warden. Count Aleksandr is the only person within the Ballroom with a weapon (sword).

Xucphr - Notice shadow movement at the far bottom-left (bottom-right corner from table-top) corner of the room. Almost as if someone is sneaking around the room.
\end{DndComment}

	Pyretrix headed over to the only Dragonborne in the room to strike up a conversation. The Dragonborne is one of the bards playing music for the guests. The bard said that Countress Katerina is “The new matriarch is one for the parties. She got the party look on her.” Xucphr move closer towards the other end of the ballroom to confirm what the moving shadows were.
	
\begin{DndComment}{Results}
Perception (5) - Probably just the candle lights near the corner causing the shadows to move around.
\end{DndComment}

Ruben approach the apprentice wizard and abjurer wizard near the center of the room.
	
\begin{DndComment}{Results}
History (23) - Notice the Abjurer wizard is actually Professor Gramwell Kestrel Moore. Known more in the field than in the classroom. He is more of a hands on learner 
\end{DndComment}

	Ruben talked to Professor Gramwell to catch up on life and the asked abut the Apprentice. The apprentice has snooty look to him; snippy attitude and look of disguest. Gramwell said "He's just an apprentice." then changed the subject. Ruben introduced Gregory, said they meet on the job. Afterwards Profressor walked to another table to talk to people about rich people stuff (economics).
	
\begin{DndSidebar}{Economics}
	Economics focuses on the behavior and interactions of economics agents and how economies work. (Results for Wikipedia. Look it up!)
\end{DndSidebar}
	
Suddenly, table crashing to the floor and screams echoed through the room. Towards the end of the Ballroom 3 assassins come out - Near The Countess and Count.

\section{Start of Combat}

\begin{DndSidebar}{Author's note}
I'm not adding all the details of the fight. That shit would be exhausting! Could add all the attacked used in combat just to practice using \LaTeX.
\end{DndSidebar}

	The assassins rush towards Count Aleksandr, Countess Katerina, and the Vampire Warden. The Warden tries their best to fight them off but luckly The Sensational Seven stepped in to help.

\begin{DndComment}{Xucphr}
Perception (21) - The vampire warden is frurious and want to end the assassins' lives. Notice the two drow standing by the warden are not worried about the assassins; Calm and demure face while everyone else look either fighten, panic, surprised, and/or angry. 
\end{DndComment}


 
	During combat, Xucphr use moment to think to find a note from the other Drow Matron Mother. The note mention that something may happen today at the Ballroom. It was signed by a person named M. The two Drow made their way towards the entrance of the Ballroom, attempting to escape. Before the group could approach the two drow they disappeared right as the last assassin was dealt with.
	
\section{Loot and Results}

\begin{DndTable}[color=PhbMauve]{cX}
	\textbf{Character} & \textbf{Loot}\\
	Xucphr & 100 gp  \\
	& Two sets of leather armor \\
	& 2 Daggers of Venom \\
	& 6 regular daggers\\
\end{DndTable}

Everyone in the party leveled up (Thank you O' Great DM)!

\section{After Combat}
	The Warden pull out a sword to torture the assassin while the familiar held him upside down while a basin is right below him. 

\begin{DndComment}{Pyretrix}
Perception (22) - Notice the rapier has “teeth” the rapier’s “teeth” almost look like a fish hooks
\end{DndComment}

The Warden took a clean stab into the side of the assassins' neck and when pulled out, ripped the flesh out from their neck. Gouts of blood rushed out from the wound and into the basin below. The Countress thanked us for our help but notice that we were not invited to the party. Decided that we mean no harmed sice we had no obligation to help in the
fight. She called us party crashers (Damn right we are and we won't stop!). 

	Warden asked for forgiveness for their lack of protection and agreed to be punishment later by the Countress. Countress Katerina ask if there’s any way she could reward us. Before the group could mention Xucphr's condition, she said there's a stench coming from Xucphr and know that we are here to rid of The Hunger within him. Xucphr mention that it has been about 2-ish week since infected (Stage 1). She said she for everyone to first enjoy the party and can help control Xucphr's condition afterwards.
	
\section{End of Session 7}
