\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}

% Use babel or polyglossia to automatically redefine macros for terms
% Armor Class, Level, etc...
% Default output is in English; captions are located in lib/dndstrings.sty.
% If no captions exist for a language, English will be used.
%1. To load a language with babel:
%	\usepackage[<lang>]{babel}
%2. To load a language with polyglossia:
%	\usepackage{polyglossia}
%	\setdefaultlanguage{<lang>}
\usepackage[english]{babel}
%\usepackage[italian]{babel}
% For further options (multilanguage documents, hypenations, language environments...)
% please refer to babel/polyglossia's documentation.

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}

\captionsetup[table]{labelformat=empty,font={sf,sc,bf,},skip=0pt}

\MakeShortVerb{|}

\lstset{%
  basicstyle=\ttfamily,
  language=[LaTeX]{TeX},
  breaklines=true,
}

\title{Journey Through Tellus \\
\large A Dungeon and D-gens Adventure}
\author{Created by Xucphr Moritz; DM by Kinetic}
\date{\today}

\begin{document}

\frontmatter

\maketitle

\tableofcontents

\mainmatter%

\part{Summary}
%PhbLightCyan for roll check
%PhbMauve for loot


\chapter{Last Session}
\section{Summary}
\DndDropCapLine{A}{fter the Sensational Seven} adventure at the bottom of the well, Pyretrix and Ruben discovered that Xucphr is infected with The Hunger. After meeting with the dark-elf clergy and receiving the Ritual of Quietness, the group traveled to Noctheria after traveling for two and a half weeks in attempt to cure The Hunger within Xucphr.

\section{Map Regions}

\DndArea{Noctheria}


\DndSubArea{Border of Noctheria}
When crossing the border, the group notice it's suddently nighttime. When crossing back, it is suddenly daytime.

\DndSubArea{Forrest}
	Heavy forest area around the village. Several bushes and grass-areas rustling as if there's something moving around, watching the village. The Sensational Seven were warned about "The Fereal One" in the forest. A fereal roar came from the forest and the horrifying sound aggitated Axe Beaks.
	
\DndSubArea{Village}
The village looks like complete and utter shit. The houses look unkept and broken down. The adventures are told the villagers are on a strickly vegetaria diet (that's bullshit but I believe it). Two trails lead towards the Matriarch of the land. One trail lead towards the forest and another takes you through a long path through the mountains.

%\DndSubArea{Building A}
%The adventurers asked for directions from the man inside the building and directed them to go to Vladmir's Keep

\DndArea{House of Orlovski}
	A masquerade ball is held at the Orlovski's estate; only one guest per house were invited. Guests are handed a masquerade mask that \textbf{must} stay on inside the house but can be taken off once outside.
	
\DndSubArea{Ballroom}
	Bards at the end of the hall playing fancy music; Classical music. Candles and lights all around. Servants appear to be frail and weak; darkness and gloom around their eyes. Guests are seen discussing political topics such as economics, eating a banquest of food all around the outside of the ballroom, and dancing with grace and class.

\begin{DndSidebar}[float=!b]{About Noctheria}
A militarized republic, led by a council of general. The capital, Stonecradle, is a mountain fortress and cannon foundary. Noctheria is in the mountains East of Tellus with a few ports and trades. It is known for flintlock militias, black steelworks, and their tactical engineering schools. The people here prefer isolation and solitude. Currently House Morvane campaigns for war with the southern nations to secure new lands.
	Daytime is 4 hours and nighttime is 20 hours.
\end{DndSidebar}

\part{Session 7's Adventure Log}
\chapter{Ballroom Blitz}
\input{Adventure_Log}

\part{Attacks During Combat}
\input{Spells_And_Attacks}


%\part{Monsters and NPCs}
%\chapter{Monsters and NPCs}
%\input{Monsters_and_NPC}


%\part{Customization}
%\input{Customization}


\end{document}
