\chapter{Ballroom Blitz}
\section{Ballroom}

\DndDropCapLine{A}{fter the assassination attempt} on Countess Orlovski. The Countess asked her guest to continue the party while her and her personal guard move to her room for rest. The guest moved around, conversation resumed, and the masquerade resumed once again.

Gregory whispered to Ruben "If we were to get every pice of meat and cheese we make a bigger sandwich than the one from the tavern!" Reuben eyes glowed and agreed to Gregory's plan. Gregory and Reuben pushed a few tables together and began to collect every food from different tables within the ballroom to their designated sandwich area.

While scrambling to every table, Reuben saw the professor again and decided to thank him for saving his life. During their discussion, Professor acknowledge Reuben's gratitude and decided to "keep his cool" for future battles. The professor also noted that Gregory is a total douche and shouldn't trust him.

Gregory and Reuben stacked so much food onto their tables that it appeared to be a large mountain. Gregory yelling at the familiars about getting more bread to complete the sandwich. After an hour of constructing this monstrosity of a meal, the sandwich is almost 6 tables in length and thickness. The sandwich was now ready to be eaten.

Gregory and Reuben's construction of the sandwich and its size caught everyone's attention in the ballroom. Bards stopped their tunes, guests paused mid-sentences, and the remaining guards all gathered around Gregory and Ruben. 

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Stealth  & 22 \\
\end{DndTable}

\begin{DndComment}{Results}
	While guests were distracted by Gregory and Reuben construction of the sandwich. Rayla sneaks outside of the ballroom to scout other rooms within the house
\end{DndComment}


Pyretrix decided to sneak a large chunk of the sandwich from Gregory and Reuben.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Slight of Hand  & 22 \\
	Ruben & Perception & 17 \\
	Gregory & Perception  & 0\\
\end{DndTable}

\begin{DndComment}{Results}
Pyretrix took a chunk of the sandwich; A very big chunk of the sandwich.
Gregory and Reuben did not notice that parts of the sandwich was missing.
\end{DndComment}


Gregory and Reuben begin eating the sandwich. During this time the entire guests paid attention
to this monster of a sandwich. Xucphr was supporting his teammates with cheers so hard, tears rained down his face and his voice echoed louder than the audience

\begin{DndSidebar}{Big-back Inspiration}
	Due to Xucphr's cheers and the crowd chanting, Reuben and Gregory gained inspiration
\end{DndSidebar}

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Table} & \textbf{Character} & \textbf{d20} \\
	1 & Reuben &  18 (CON Save)\\
	& Gregory &  20 \\
	2 & Reuben &  16 \\
	& Gregory &  18 \\
	3 & Reuben &  7 \\
	& Gregory &  12 \\
	4 & Reuben & 5 \\
	& Gregory &  9 \\
\end{DndTable}	

Reuben and Gregory ate two table-worth of the sandwich before feeling the pain within their stomach. They struggled pass the third table as their stomach kept expanding. As the guests continue to cheer and chatter about the sandwich, Reuben and Gregory made it to the fourth table but they stopped. The two felt something within their bellies attempting to release itself from their mouth; They've almost reached their limit.

\begin{DndTable}[color=PhbLightCyan]{cXX}	
	\textbf{Character} & \textbf{Skill}  & \textbf{d20} \\
	Reuben & STR Save & 18 \\
	Gregory & STR Save & 28 \\
\end{DndTable}

Reuben and Gregory were able to stop the food coming up from sheer strength and willpower.
Reuben and Gregory went in on the last 3 tables. The guests were seen making bets, exchanging money, and cheering on the two adventurers as they continued to eat. 

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Table} & \textbf{Character} & \textbf{d20} \\
	5 & Reuben & 5 (CON Save)\\
	& Gregory & 23 \\
	6 & Reuben & 17 \\
	& Gregory & 23 \\
\end{DndTable}


Reuben and Gregory finished the sandwich. There was a sudden loud roar of cheers and celebration around the adventurers. The guests we're flabbergasted by the amount of food that was consumed in such a short time. 


\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Investigation  & 19 \\
\end{DndTable}

\begin{DndComment}{Results}
	As the entire ballroom is distracted, Rayla sneaked out and heard two guards discuss the mountain sandwich that was eaten by Reuben and Gregory. Afterwards they talked about
	the assassination attempt was a failure; unsuccessful. They talked about another assassination attempt to the Countess.
\end{DndComment}

Rayla notice that the halls are very empty; at least a servant would be around working.
Most of the doors are locked except for one unique ordained door.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Perception  & 20 \\
\end{DndTable}

Rayla listen to the door and heard "screaming nature". Pain noise and whipping sound. Also sounds like the Countess chastising someone. Verbal torture and how the person failed her today. The person responded "It will not happen again" and "Yess my Countess".


Xucphr is amazed by Reuben and Gregory and wanted to know if they want to try 12 tables next. They responded "Damn right we'll try it!". Pyretrix went around and apologized on behalf of the team and the aristocrats were happy about the ordeal.

The familiars were planning to eat the leftovers from the party but Reuben and Gregory at all the food at the estate.
The familiars are going to be starving; At least 12 familiars. Pyretrix gave away 6 of the rations to help them. 
Pyretrix took some rations for Reuben and was able to provide 12.

All the familiars went to the back after collecting the food, then came back out to give Pyretrix a big bottle of what appears to be a drink.
Pyretrix drunk some of the drink and gave the sandwich that he took.

Pyretrix and Xucphr help Reuben and Gregory to the room in the back to rest. The room in the back was very nice. Every bed was a California king size bed.
Very comfortable. The minute you lay in the bed you sink into it.
"Ring the bell and one of us will come" said one of the servants before leaving the room.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & Perception  & 18 \\
\end{DndTable}

\begin{DndComment}{Results}
	Xucphr checked the room for any traps or spells that were waiting for them. No traps nor trickery in the room
\end{DndComment}


Rayla still looking around, went downstairs
Rayla hear whimpering and cries behind some of the doors.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Stealth  & 21 \\
\end{DndTable}

\begin{DndComment}{Results}
	Rayla slowly opened the door that no one in the room would notice her.T here are cages and there are several individuals who are connected to a device that make them constantly bleed.
	About 30 people in the room. 
\end{DndComment}

Rayla came back up to talk about what she saw.The familiar stumbled from hunger. Rayla then continue her investigation.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Perception  & 23 \\
\end{DndTable}

\begin{DndComment}{Results}
	Rayla look upstairs and found 7 guys and one girl in a room. The two familiars that familiars saw were female, the one Pyretrix saw were men. The people Rayla saw were all men who were bleeding out
\end{DndComment}

Afterwards the adventurers went to their rooms and rested for the night

\section{Long Rest}

Familiars came to our room and greet them in the morning.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & Perception  & 19 \\
	Rayla & Perception & 23 \\
	Pyretrix & Perception & 11 \\
	Reuben & Perception & 2 \\
\end{DndTable}

\begin{DndComment}{Results - 10}
	Familiars that came in have bandages with fresh blood stains on their neck.
\end{DndComment}

Familiar licked his lips after providing drinks and walked out before Pyretrix could offer some drinks. Familiar came back with two massive pastries, coated in chocolates and jelly filling, and earl grey tea.


Pyretrix put a hand on the familiar for thanks and the familiar flinches.

Pyretrix decided to split the pastries with the familiar and to ask a few questions.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Intelligence  & 12 \\
\end{DndTable}

\begin{DndComment}{Results}
	Pyretrix would know that feeding an excessive amount of calories would kill him.
\end{DndComment}

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Intelligence  & 1 \\
	Xucphr & Intelligence & 18 \\
\end{DndTable}

\begin{DndComment}{Results}
	Pyretrix was able to give the familiar enough food to not kill him
\end{DndComment}

Pyretrix asked the familiar what can you tell us about the people chained downstairs

Familiar looked at us and said "It is the tides"
"Could you elaborate?" Familiar showed his neck and showed two punctures on the side of his neck. "We give and we are gifted with everlasting life if we survive". Majority are there willing, while the rest are criminals: murder and thieves. The criminals are bleed dried.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & Perception  & 15 \\
	Rayla & Perception & 19 \\
	Pyretrix & Perception & 8 \\
	Reuben & Perception & 16 \\
\end{DndTable}

The Sensational Seven suddenly heard yelling in the hallway. We hear the female familiar yelling at a male familiar and switch languages
"The countess has been looking for you". 
Afterwards the female familiar walked away really fast. 

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & Perception  & 12 \\
	Rayla & Perception & 9 \\
	Pyretrix & Perception & 6 \\
	Reuben & Perception & 8 \\
\end{DndTable}

The group of adventurers were attempting to chase after her but was unaware of her direction due to how fast she left the hallway.

After the lashing, No kept moving and we tried to stop him.

Women here are the only ones who can ascend the levels of matriarch. Men can only stay servant.

Alexander of Orlovski is the greatest swordsman in the land
No seems like they are ok with the lifestyle here.

Rayla keep asking about Solstice and how to be come a citizen.

Reuben wake up Gregory so that we can go to the Countess about Xucphr's hunger

Familiar take us to Countess and went to a very big room where everything is red, black, and gold
She's in a really nice formal nightgown.

All the wounds she suffered was gone. She recovered
Countess complimented Rayla's outfit

Countess told Xucphr "walk with me" and she start discussing about the hunger.
As walking by, she explained the history of vampirism
Vampirism comes from the hunger
It was a way for the people of this land to take the hunger and instead of consuming them,
they beat it into submission and made it into something beneficial. The curse of the hunger became the blessing of vampirism.
There's a very extensive/dangerous ritual to subdue the hunger without becoming a vampire. It's very wishy-washy
If it doesn't work then the hunger becomes worse. No idea what the changes of the ritual succeeding 

Can become:
Scion of count Orlovski and can go about my way. At the end of the day, Xucphr belong to her

The Countess said she doesn't mind sharing. Xucphr agreed to the Countess deal.
Rayla want to turn into a vampire.
Countess get out whip and said "Come with mommy". Alexander is there to witness everything


Alexander points to everyone and said "you must all stay your hands"
When you see what happens next, you are not to act.


We asked for No to receive the gift as well since we think he deserve it.
No comes over to the Countess, size him up, and says "Very well"

We found out Werewolves exist and must come into contact to be turnt.

We go into a hidden chamber. The chamber is very vampirish (stereotype)
She walk over to the basin and take her index finger, jam it into her forearm and drag it to the palm of her hand.

She let the blood fill the basin before she heals it back up.
"Not a drop can be wasted"
The three of us start drinking and emptied the basin.
Alexander tell us all the back up, except for the three.
Draw his sword and stands there, afterwards Countess points to three servants and slit our throats; beheaded us

All 3 fall onto the ground dead
The color of the body fade, bodies start to convulse violently.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & CON Save  & 5 \\
	Rayla & CON Save & 24 \\
\end{DndTable}

\begin{DndComment}{Results}
Rayla and No stopped
Xucphr continues to convulse violently

Xucphr fingernails grows into talons
Gained secondary fangs, Tusk is larger
Xucphr look more beastly than the other two.
\end{DndComment}


\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & CON Save & 17 \\
\end{DndTable}

\begin{DndComment}{Results}
	The convulsion stopped for Xucphr.
\end{DndComment}

Eyes are glowing red, look pale. 
No looks fit. Looked scrawny. Went from 5'3 to 6'2; Like captain american during treatment.
All gained blessings of the vampire. Gain two levels of exhaustion.
Take a long rest and a feeding or two long rest.


Countess said "You must be famished. Please come" She walks back to her room and poured out a decanter 
Pour a glass for Xucphr, No and Rayla.
Alexander asked for the Countess.
Countess: now for the introduction into House of Orlovski

Xucphr Moriz of Orlovski
Rayla of Orlovski
No of Orlovski

No will be part of the breeding stock.
Rayla said we have to find two coffins and cloaks
Given leather armor and Black steel coffins
AC of 19

Pyretrix asked a couple of questions about evil witches.
Countess said Rayla's homeland is full of fae magic
She's from lorenthar and the king's daughter

Rayla asked the Countess asked where we could find cloaks to go into the sunlight
Countess said we could go to Thalvarien

Coutress provided 4 blood bottles to Rayla.
Countess knows everything about us and our past.
Other ways of communication

Not able to wander around the cities unless you're under a house.
Night wardens watch over the matriarch in night. 


\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & Perception  & 9 \\
	Rayla & Perception & 19 \\
	Pyretrix & Perception & 12 \\
	Reuben & Perception & 16 \\
\end{DndTable}
\begin{DndComment}{Results}
	When Alexander hear Countess said "We're her savior" he looks sad, then turn back to stone faced
\end{DndComment}

Suzanna the familiar will be able to escort Pyretrix and Ruben.
Rayla asked if she could tell us where the magic shops are.
She takes us to a couple of stores.


As we were traveling through the town. One of the magic shops had a familiar wand
The barter wanted to 
Rayla bought the wand of impossible girth for 20 gold pieces


Time skip back to town
We creep back into sleepy town
it is the middle of winter and the town look more rundown than it use to be
People outside look like they're having a rough time
We came to Cookie tavern and it is gone ( destroyed)

Someone in front of the tavern and placed flowers
As we get closer Kara is pregnant
Kara with child was cried and told us about the tavern burned with cookie inside.
The duchess burned the building down while he was inside. Cookie wouldn't pay any more taxes.

The daughter kept begging cookie to pay the taxes. 
The twins survived but left town. They couldn't bear to stay around


The duke was executed and the duchess took control.
Duchess got a new advisor - looks human - named agosh

Kara confirmed that the duchess took over the town and raised taxes like crazy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


	
\section{End of Session 8}
