\section{The Keep - Throne Room}

\DndDropCapLine{R}{ayla, Pyretrix, Gregory, Nova, and Ruben} are under the Greater Succubus' nightmare trance while Brolasi and Xucphr unaffected. Brolasi and Xucphr saw their companions eyes turn pitch-black dark and unresponsive. They demanded their comrades to be free but the Greater Succubus was more curious about how the two were unaffected. "I'm quite curious how you two aligned yourselves with a higher power", said the Greater Succubus. Brolasi and Xucphr decided to risk fighting the Greater Succubus and his minions to save their friends.

\section*{Start of Combat}

\begin{DndComment}{Full Combat Details}
	I'm not writing out all of that shit. If you need more details, the raw notes can be provided.
\end{DndComment}

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Const Save  & 15 \\
	Rayla & Const Save & 10 \\
	Ruben & Const Save & 19 \\
	Nova & Const Save & 19 \\
\end{DndTable}

While Xucphr and Brolasi defend their companions from the hell hounds, Pyretrix, Nova, and Ruben broke out of the nightmare and assisted Xucphr and Brolasi. Rayla and Gregory are still in a trance.

While the fight continued, Xucphr shot at the night hag to leave Kara alone. The night hag pointed to Xucphr and said "Kara...." in a low, raspy voice. Xucphr eyes widen and she suddenly disappear.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Gregory & Wis Save  & 2 \\
	Rayla & Wis Save & 19 \\
\end{DndTable}

Gregory is still in a state of ecstasy from the trance while Ruben attempt to wake him up. Rayla was able to break free and started to attack Commander Listeria.

The Greater Succubus melted his body and became one with the duchess' body, becoming possessed. They combined to become Duchess Solaran the Ascended. The night hag reappeared, pointed to Xucphr, and said "Kara" before she disappeared again.

Sid, the Notary Devil, walk behind Pyretrix to offer a contract that will benefit him during the combat. "If you sign this contract offering me your eternal soul when you die, with no influences, you can get your weapons back" Pyretrix passed up the bargain as he was attacked by several hell hounds. While fighting for his dear life, Pyretrix agreed and signed the contract. Right after the last stroke from the pen, his great axe appeared in his hand. 






\section{End of Session 9}
