\chapter{Journey to Thalvarien}
\section{On the road}

\DndDropCapLine{P}{yretrix have a map in his hand} and started to move in a direction.
Pyretrix seems to have convidence in his sense of direction.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Check  & 1 \\
	Pyretrix & Survival & 18 \\
	Brolasi & Survival  & 15 \\
\end{DndTable}

Pyretrix realized after 2 days of traveling that he lead the group in the opposite direction of Thalvarien.
Pyretrix told everyone to stop moving and brough Ruben over to explained the situation. Ruben realized that the map is upside-down.
Ruben is upset that the group wasted 2 days of traveling. Pyretrix tried to blae Ruben but their argument grew louder and louder.

The rest of the group overheard their conversation about traveling for 2 days in the wrong direction.
Pyretrix said we can turn back around in the opposite direction to get to Thalvarien.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Check  & 11 \\
	Xucphr & Animal handling & 22 \\
	Pyretrix & Animal handling & 1 \\
\end{DndTable}

The Sensational Seven were able to get back on track for Thalvarien but they lost two days worht of time.
There was a lot of stop and go during the trip. Everytime Pyretrix take the lead the axebeaks attacked each other.
Sometimes the axebeaks would hit and miss; A few times they tried to kill each other. 
Brolasi bloked the axebeak's attack and realized they do not like Pyretrix.

The adventurers pass through the forest and found a nice town to stop for the night.
The town is tiny with 5 buildings; two houses, a general store, a potion shop, and a tavern-like building with "Clean food and water sign"

\section*{Tavern}
Pyretrix, Ruben, Xucphr, and Brolasi struggled to get through the tavern door due to it's small size.
A man behind a makeshift countertop look like a gnome. He spoke somewhat like a heavy russian accent and very fast.
The man look at us with an emotionless expression.
Judging from his face, not many people pass throguh the tavern.

Xucphr started the ritual for comprehend languages. 
While Xucphr chanting in tongue, his eyes roll to the back of his head as he's levitating.
Brolasi goes to the bar to get a drink. THe man comes back out with a mug with brown liquid and set it in front of them.

The drink does not taste like beer. It taste like he something he made up on the spot.
The drink is not good and not strong enough to get someone drunk.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Brolasi & Deception  & 19 \\
\end{DndTable}

Brolasi gave the bartender a half-hearted smile with a thumbs up.
The bartender's expression changed from black to excitement. He smiled back at Brolasi.
Xucphr still chanting with his eyes in the back of his head.

\begin{DndSidebar}{Xucphr's Chant}
	Xucphr's chantting, levitation, and expression scared the entire tavern.
	He's literally scaring the wenches!
\end{DndSidebar}

Pyretrix start walking around the town. Pyretrix stare at the people in the town to see if anyone will attack the group.
There are a few children that appear depressed. 
Everyone in the town seem to live a decent life; no homeless situation and everyone live in a nice house.
The general store and potion shop look a bit worn down but very lively.

The potion shop is ran by a minotaur named Sebastian Steer. 
General shop appears to  be ran by a Giff (hippo people). Pyretrix decied to walk into the potion shop.
The potion shop appears bigger than the other stores around town. Ruben and Rayla head to the potion shop as well.

Sid appears right next to Pyretrix and Pyretrix jump a bit back.
Pyretrix talked to Sid about trading someone's soul for his soul, which Sid rejected the "soul for a soul" idea.
Sid said the contract is binding and won't alter the contract.
Sid explained that he can't kill his brother but Pyretrix is very strong and should be able to kill him.
As Pyretrix tries to alter the contract, Sid's eye start to twitch from fustration.
Pyretrix asked if there was a way Sid can move the group closer Thalvarien.

The rest of the adventurers saw Pyretrix talking to himself; they're not able to see Sid.
Only one other persion and Sebastian heard Pyretrix within the shop.
Sid began to cry and rant about his eternal tormenting from his brother; tortured for the past 10,000 years.

Sid mention that a subclause was to be added if he doesn't ill his brother and can take his soul.
Sid an Pyretrix agreed that someone can take Pyretrix's soul in place but he \textbf{MUST} kill Kip.
The two shook hands and cains wrapped around their hands.
Sid demanded that he has to kill his brother in front of him; Promised to throw in an extra reward.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Perception  & 15 \\
\end{DndTable}

Rayla and Ruben stared at Pyretrix while Sebastian stared at Pyretrix and well.
Sebastian stated that Pyretrix was talking to himself and was amazed by his conversation.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Stealth & 17 \\
\end{DndTable}

Sebastian spoke to Ruben and offered to smoke some gnome weed in the back room.
As Ruben and Sebastian made their way to the back room, Rayla stole all 15 potions from the shop.
Pyretrix tried to find a way to fix this issue if Sebastian realized the stolen potions from the shop.

In the back, Sebastian brought out a gravity bong. It look like a masterpiece where orbs gravitating around the bong.
Ruben was amazed; a single tear of joy fell from Ruben's eye.
Sebastian pulled out the weed but it was no ordinary weed. This was enhanced gnome weed, a Thalvarien type gnome weed.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Ruben & Const Save & 14 \\
	Ruben & Const Save & 20 \\
	Ruben & Const Save & 18 \\
\end{DndTable}

Ruben took several puffs and the effect started to hit him. 
This is one of the best weed that Ruben ever had in his entire life. 
Body tingle, open mind, and super relaxed.
Ruben was in a Nirvana state with his eyes glowing and body levitating from the ground.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Const Save & 21 \\
	Rayla & Const Save & 24 \\
\end{DndTable}

The amount of weed Ruben and Sebastian smoke created a weed cloud that spread inside the shop.
Rayla and Pyretrix hurried to leave the shop befoore the weed cloud hit them.
As Raylay and Pyretrix successfully left the shop, an elder man outside the shop said "He really need some help" before walking away.

Back at the tavern, Xucphr's ritual finally finish and returned back to normal.
Xucphr was able to understand the bartender and asked him about the town.
"It's a very small town, not welcoming and I wish to die.", said the bartender.
"The paladian that walked in and drank my drink made me happy at least." as he smiled towards Brolasi.
Brolasi just gave a half-hearted smile back.

The bartender, Peter, explained that the town treated him like shit and hated the drinks that he served.
He mention that he ws a worshipper of the not good ones - the ones down below. 
Peter was a cultist of the nine hells that trid to resurrect a creature of darkness.
Due to the several unsuccessfull resurrection he left them behind.

Pater does not keep in contact with the cult after a long period of time.
He said there's plenty of cultist spots in Thalvarian, even some in Noctheria.
Xucphr told Peter to stay there as he left the tavern to find Pyretrix. 
Xucphr saw Pyretrix and both adventurers ran straight to Peter in the tavern.

Peter greet Pyretrix and offered a drink. Before Pyretrix could answer, Peter went into the back and brought out a mug with brown liquid.
Pyretrix drank from the mug and realized the drink tasted aweful, thinking that this is what dirty toilet water taste like.

Pyretrix finised the drink and said he's never had a drink that's also chewey.
Peter explained that he made a drink that's also a meal at the same time.
Pyretrix said "Well Sid would like this drink and he's a demon". 
Peter asked if Pyretrix was threatening him while looking in disgust from Xucphr and Pyretrix.

Pyretrix stated that he can hook Peter up with Sid.
"What part of the nine hells this Sid stay in?" said Peter.
Pyretrix didn't know but Peter said pick a number.
"Sid is from the Iron City of Dis" Pyretrix responded.

Peter has visit the city once but enjoyed his experience with the city.
Peter agreed to Pyretrix's deal but did not know how to create the pact.
"You may need to shake his hand. It worked with you and Sid before." said Xucphr.


Once they shook hands, chains wrapped around Peter and he fell downward into a fiery pit.
Pyretrix body felt heavier and felt relieved that his soul returned.

\begin{DndSidebar}{After The Handsake}
Every on the tavern saw Peter fell into the pit as he screamed for his life.
Between Xucphr's ritual and Peter's descend into hell, everyone in the tavern kept their distance from The Sensational Seven
\end{DndSidebar}

Pyretrix called Sid and he appeared to Pyretrix once again. Sid confirmed that Peter soul ws taken and Pyretrix gain his soul back.
Suddenly Sid became visible to everyone in the tavern. "Hell gained another person who belong there" said Pyretrix.
Sid told the group that their brother, Kip, has a contract with someone in the city - Yotash Nemmonis.

\begin{DndComment}{Demon Cheeks}
Sid offer Pyretrix a quick feel but Pyretrix declided the offer.
Rayla cop a feel on Sid's butt - firm but smooth.
\end{DndComment}

The group decided to head to the potion shop to get Ruben.
A giant weed cloud that covered the entire potion shop with no safe way inside.
Rayla decided to enter since vampires are immune to thw weed cloud.
Rayla crawl around the shop due to the thickness of the smoke.

Rayla successfully made her way into the back and viewed Ruben and Sebastian floating mid-air and glowing.
Ruben and Sebastian were having a deep conversation with all of the gods within their gnome-weed trance.
Rayla attempt to speak to Ruben but no response. She tap Ruben shoulder and his entire dream fell apart.
Ruben is broken out of his high and was upset. Rayla told Ruben it's time to head out.

Before leaving, Sebastian gave Ruben a big bag of enhanced gnome weed. Sebastian and Ruben dap each other before parting ways.
Brolasi requested Ruben to share the enhanced gnome weed but Ruben said he will share it once the time is right.


\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Check & 22 \\
	Xucphr & Animal Handling & 19 \\
	Brolasi & Animal Handling & 12\\
\end{DndTable}

The Sensational Seven head out towards Thalvarian after leaing the small town.
Pyretrix guiding the group and making great progress.
The axebeaks attack each other again but the situation was handled easily.
Roughly a week worth of travel to Thalvarian now; It is currently dusk

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Perception & 6 \\
	Xucphr & Perception & 19 \\
	Brolasi & Perception & 18\\
	Rayla & Perception & 23\\
	Nova & Perception & 20\\
\end{DndTable}

The adventurers notice a campire as if it was on the path from a distance.
As they approach the campfire, they found a few tents with women.
The women have the same color tones and armor, most likely a mercenary group.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & History & 9 \\
	Xucphr & History & 18 \\
	Brolasi & History & 11\\
\end{DndTable}

There's a flag with a crown and symbol by the campsite. Brolasi and rayla introduced themselves first.
They notice the females were very brawlic; A centar with a war hammer, a dwarven with a sattle, and two other women.
Xucphr caught on that the buffest person was a changling and the other is a shifter.

Brolasi introduced themselves to the changling named Valna.
Valna explained that it's been ages since their group had civil conversation with people and asked the reason for our traveling.
Brolasi stated that we're on a journey for their friend Pyretrix. 
Valna reached into their bag and brough out a strip of leath with writing.
"If you need anything, you can alwasy hire The Queens!" said Valen.

Valen further explained that The Queens are a mercenary group that were finishing a security job for some rich person.
Valen mentioned that Ilkari, the shifter, was something else during their last job; Ilkari was insulted and started to argue with Valen.

They walk over to the fire and brought out some rabbits and whatever else they had in their bags.
Brolasi brought out some rations to share with The Queens. Ilkari walk towards Pyretrix and ask to arm wrestler to see how strong he is.
Pyretrix and Ilkari sat at the table near the tents, sat down, and grab each other hands.
Pyretrix and ilkari's veins were popping from their hands.

\begin{DndSidebar}{Size Up-09}
	When Ilkari walk towards the table with Pyretrix, they were at least 3 inches taller than him.
\end{DndSidebar}

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Check & 22 \\
	Pyretrix & Check & 18 \\

\end{DndTable}

The strength between Pyretrix and Ilkari was intense, both were evenly match in the arm wrestling.
"Oh this one got some meat" said Ilkari. 
Rayla, Xucphr, and Ruben place bets on who would win between the two. Some of the other members of The Queen place bets as well.
Suddenly, a loud slam from the table echoed through everyone's ears as Ilkari defeated Pyretrix.
Ilkari wanted another round with Pyretrix, to which he agreed as the two were enjoying the competition.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Check & 11\\
	Pyretrix & Check & 18\\
\end{DndTable}

Once again the two were evenly match in strength. The Queens and The Sensational Seven continued to cheer for their respective teammates as the match went on.
A few minutes later, Ilkari slam Pyretrix hand to the table and the match was over.
"It's alright little one. I still had fun." said Ilkari as they walk away and started to chant.
The two groups started to drink and enjoy the festivities.

Ruben was hanging around the fire, relaxing and enjoying the drinks.
Pyretrix was leaning against a tree near the campfire, watching everyone having fun.
Brolasi haning by the fire and smoked some gnome weed they stole for Ruben.
Rayla drinking some vampire wine and sitting near the fire.
Xucphr is partying with the ladies and enjoying himselves with the festivities.
There was a hint of jealously from the countress that Xucphr felt throughout the duration of the party.

Ilkari walk towards Pyretrix with a mug of stright whisky and said "Drink like The Queens today!".
Pyretrix and Ilkari chug the drinks then Ilkari punch Pyretrix arm, in a friendly way, and said "YUEAH!".
"I haven't had a hard time like that in a long time. I enjoyed myself." said Ilkari as they brought out more mugs of whisky to drink.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & Perception & 13 \\
	Brolasi & Perception & 20\\
	Rayla & Perception & 19\\
\end{DndTable}

Xucphr, Brolasi, and Rayla notice that these women are very dangerous. 
Outside of the camp area there is no danger. The only danger is from The Queens.
As the festivities started to end, Rayla and Ilkari take first watch for the night.

Ilkari pulled out a big thing of Whisky to drink and talked about the party.
Rayla also pulled out a drink and they click glasses together.
Ilkari talked about how she removed a guy's head from his shoulder in 10 seconds, spine and all.
Rayla reached out and squeezed Ilkari's muscles; solid and firm touch. Ilkari mention that they can change all of their body parts

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Persuasion & 24\\
\end{DndTable}

Ilkari sand that it's time to switch out and it's starting to get cold. Rayla wanted to know if there's any room in Ilkari's tent for her.
Ilkari and Rayla went back to the tent for the rest of the night.

Ruben and the dwarf, Pigsly, were next to watch over the campsite. 
He offered gnome weed to the dwarf mercenary and wanted to know more about The Queens.
Xucphr was attempting to get out of his coffin but Ruben sat on top of the coffin to prevent him from leaving.
Pigsly mention that everyone in her squad is strong but reassured Ruben that she is just as strong as the others.
Ruben also reassured her that he's as strong as his team with his spells. 
They continued to talk until their shift was over. Ruben continued to sit on top of Xucphr's coffin.

\begin{DndSidebar}{It should have been me!}
	Xucphr was understanding but upset that he didn't get a chance to interract with the muscle mommies.
\end{DndSidebar}

Ruben was exhausted from watching Xucphr for the entire night. Rayla and Ilkari kept going with their "pillow talk" the rest of the night.

Brolasi and Valna take the next watch and Valna mention that the ladies need some entertainment and joy every once in a while.
Valen stated that The Queens are heading back to Thalvarian to make another coin for themselves.
Brolasi asked about making a deal later in the morning to fight a devil. Valna agreed and the two talk until sunrise.

Around 7am, everyone started to wakeup and start their day. Rayla and Ilkari just finished their fun around 4am.
Rayla said she gave Ilkari a run for her money but Rayla was walking funny the entire time; Ilkari is also walking funny.
Ilkari said they wanted to find her next time it's "cold" but Brolasi said as long as we pay them we can call on The Queens for help.
Rayla walk over to Ilkari and talk about hiring The Queens for their journey.

Valna said she knows Ilkari had a great night but anything dealing with finances has to involve her.
The price for The Qeens is 2k gold per person per day. Ilkari said they'll take any kind of payment but Valna shut down Ilkari's statement.
Then Valna reached into her bag and pulled out a leather strip. "Our card" said Valna as Brolasi took the "card" from her.
The leather strip contain their location in Thalvarian and their symbol.
The queens started to pack their things and leave the campsite. Ilkari gave Rayla a kiss before they leave.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Check & 15\\
\end{DndTable}

The Queens went off path to hunt for some food as The Sensational Seven continued their path to Thalvarian.
Pyretrix turned a 1 week trip to a two week trip due to terrible sense of directions.
The adventurers ran into a few enemies but nothing the team couldn't handle.

\section*{Thalvarian}

The Sensational Seven made it to the city and were amazed by the view from the outside.
Thalvarian is a stipidly large city state. Walls built all around the pyramid-like shape town.
White marbel buildings and big booming businesses with the streets filled with townspeople.
The blackpowered and government business were expanding and booming; It is the golden age for industry.

The adventurers made it to the fornt gate and see the guards. 
The gates had vines of bronse and what appears to be leaves made of gold.
The guards have swords, shields, and double barrel shotguns while the smaller guards have maces and other small weaons.
"Business or pleasure" said one of the guards and he look around the carriage.
Another guard asked about the crutters, Ziggy and the axebeaks, and mention that we're responsible for our own creatures and held responsible.
The Sensational Seven understood and paid 5 gold pieces for each person and 10 for each animal.

The guards open the gate and said "Enjoy Thalvarian" as they move aside for the group to enter.
As the group went inside, the adventurers took a moment to absorb their surroundings.
The roads were paved, which is not a common view, wide sidewalks, and steam machines around every corner.


Rayla and Xucphr decided to head towards a jewerly store to get some gold coins for the jewerly in Xucphr's bag.
They found a shop called The Dragon's Hoarde and see a halfling at the register and a few other people working with customers.
Xucphr talked to the halfling at the register and wanted to trade a Ruby for some gold.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Perception & 14\\
	Xucphr & Perception & 7\\
\end{DndTable}

The person at the counter seem like a good person. Xucphr can tell it's a professional establishment.
Xucphr let the person behind the register see the ruby. The man offer Xucphr 2000 gold pieces for it and Xucphr agreed.
Then Xucphr use Moment to Think to take the Ruby back from the shopkeeper and put the Ruby back in his bag.
The shopkeeper was embrassed that le lost the Ruby but Xucphr offer the exact same Ruby for 4500 gold pieces.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & Persuasion (A) & 20\\
	Xucphr & Persuasion (A) & 26\\
\end{DndTable}

The shopkeeper said he needed to make up in sales for the Ruby he lost and offered 1500.
Xucphr refused to budge with his offer and told the shopkeeper that he'll make his money back.
The shopkeepr caved in a bought the Ruby for 4500. Xucphr also offered an Opal for 800 gold pieces. Once again the shopkeepr refuse to buy at that price and offered 500 gold pieces.
Xucphr iron steel will made the shopkeepr cave-in for 800 gold pieces.

Meanwhile, Ruben decided to meet an old friend and head towards their residence. 
He walked up to the door, knocked, the rush quickly to the side of the door.
An explosion was heard from inside the house and a big lead ball went straight through the door.
Inside, a red dragonborne pop their head out from the door and said "Ruben, I'm still working on your weapon!"
Namash Drephac, the dragonborne, told Ruben to come into the house and look out for the traps.
He asked Ruben about his latest adventure while he's working on the weapon.
As Rubne talk about his adventures a small explosion happened and Namash's face turned black from the gunpowder.

Ruben discovered that the top part of his pinky was gone. Namash said it was all a part of science.
After catching up, Namash told Ruben his weapon would be ready in 3 days. 
Namash escort Ruben to the front door and continued to tinker away.

Brolasi and Pyretrix head towards a tavern called "The One-eyed Beholder" where they meet a beholder behind the bar with no eyesockets.













\begin{DndSidebar}{Added Lore}
	It was declared by the DM that Pyretrix will be the uncle of Xucphr's child. 
\end{DndSidebar}

\section*{Loot and Results}

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{item(s)} \\
	Rayla & +5 Potions (Remaining after sharing with the group)\\
	Ruben, Pyretrix, Brolasi, Xucphr, Nova & +2 potions (from Rayla) \\
	Ruben & Enhanced Gnome Weed (20 usage) \\
	Rayla & +10 Gold (Betting)\\
	Xucphr & +10 Gold (Betting)\\

\end{DndTable}

\section*{End of Session 11 - Level Up}
