\chapter*{Journey to Thalvarien}
\section{The Bejeweled Tits}

\DndDropCapLine{A}{t the club,} Rayla went towards the bar to grab a drink and some food.
The bartender had no food but offer Rayla a Celesteral Sunshine.
She asked about the dragonbore on the stage and the bartender told her that his part of the Nemmonis family.
"He's part of the high society but is usually with the lower lives." said the bartender.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Perception & 16 \\
	Rayla & Performance & 26\\
\end{DndTable}

Rayla notice the imp behind Kavash flying side-to-side and she was enjoying the music.
Rayla and Ziggy hit the dance floor and both started to bust some serious moves.
Kavash started placing faster but Rayla was able to keep up with him playing.
THe entire club were watching the two fierce performance.
When the music ended, Kavash was very pleased with the performance from Rayla.

\begin{DndSidebar}(Dance Inspiration)
	Due to the intense performance between Rayla and Kavash, Rayla gain heroic inspiration.
\end{DndSidebar}

Afterwards, Rayla head towards the bar to grab a drink after the intense dancing her and Ziggy performed.
The bartender told Rayla that Kavash wanted to meet her in his private booth.
Rayla head to Kavash's private booth and he and the Imp, Melphina, welcomed her.
Rayla and Kavash talked about music and Kavash's talent.
Melphina mention that Kavash write and play all the music.

Meanwhile, the rest of the team are at the tavern and turned in for therest of the night.
Xucphr decided to watch over the tavern from the outside.
The night was peaceful with no immediate danger lurking around.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Con Save & 13 \\
	Xucphr & Perception & 5\\
\end{DndTable}

Kavash enjoyed Rayla's company that he gave her a piece of paper with arcana runes and told her that she is welcomed anytime to his place.
The piece of paper contain the spell Return that is a one time usage to go to Kavash's place.
Rayla and Kavash drank so much that Rayla blacked out for 3 hours. 
Rayla woke up and discovered she was in a different room; Fancy bed, silky pillows, and a large chandelier attached to the ceiling.
Ziggy was knocked out but look happy. Kavash was sleeping in a love seat on the side.
Melphina came in, greet her, and came back with frood and drinks from the kitchen.

Melphina said that they're currently at the top of the archive tower in the schoo. 
Then Rayla took a sip of wine and her hangover headache receded.
Melphina said that Rayla was with her and Kavash having fun around the town and Rayla purchased a 500gp dress with very nice pockets from the store.
Melphina also mention that Rayla explained that she is a bloodsucker and made up a team named The Bubble Buddies in her advantures.

The piece of paper Rayla received is a one time usage and to use it wisely; It's a teleportation spell for kavash's room
Kavash has a teleportation cirlce in his room so he can teleport anywhere within town.
Kavash gave Rayla an umbrella to protect her from the sun and used the teleportation circle in his room to take her to the tavern.
Rayla appeared at the front of the tavern with a new dress, umbrella, and reek of alcohol.

\section{The One-Eyed Beholder}

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Ruben & History & 13 \\
	Ruben & History & 19\\
\end{DndTable}

The rest of the team assumed that Rayla was going to the library at the school and thought she was missing.
Rayla explained that she was partying with Kavash and Melphina all night.
Ruben know of Kavash and Melphina and due to trauma he open his bag of holding and scream into the bag. 
Rayla mention that while she was partying with kavash, he crack someone's skull with his violin and they could be dead.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Pyretrix & Con Save & 12 \\
\end{DndTable}

Rayla said that Kavash would help Pyretrix out of the deal with Sid but Ruben know that Kavash is lying to her.
Pyretrix want to leverage Rayla and Kavash relationship but rayla refuse to help.
Ruben suggest to talk to Yotash at the college instead of involving Kavash.
Pyretrix have a migraine from Rayla defending Kavash and Melphina.

Rubem mention that the college have tours for the school, but only wizards are allowed.
Brolasi is abe to join Ruben at the college with a potential "charity" group from the church.
"There's only one teacher that we'll have to avoid" said Ruben. Brolasi wasn't worried and still decided to join Ruben.
Xucphr summon Ta'lisk, his imp familiar, to pose as Ruben's familiar.
Ta'lisk have a handlebar mustache, a bow-tie, and a small top hat tilted to the side.
Xucphr said that he can use Ta'lisk to communicate while he's at the tavern.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & Investigation & 13 \\
\end{DndTable}
Before Rayla left the tavern, she let Ruben borrow the sending stone for the mission.
Rayla became lost in an attempt to find the location where Kavash killed a patron.


\section{The School}
\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Ruben & Stealth & 10 \\
	Brolasi & Stealth & 0 \\
\end{DndTable}

Ruben and Brolasi made it to the school gate where Ruben was flooded with memories of the school.
Brolasi and Ruben were terrible sneaking around the school; they were caught by the Dean.
Dean Alistair Vornhal is a small gnomish land, with a top hat and 3 ft. tall.
Ruben is suppose to be out of the school for an assignment but Ruben apologize for not checking in.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Ruben & Perception & 23\\
\end{DndTable}

Ruben introduced Brolasi as their note taker and Brolasi mention that this is charity work from the church.
Dean Alistair said that he heard about the church and their efforts. 
He offer a generous donation for "Monks for Punks" charity.
Dean Alistair said Provessor Vivarian want Ruben to return from his assignment and attend the school.
Ruben explained that he learned more from his journey than the school and cast Protection from Good or Evil on Brolasi.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Ruben & Deception & 6\\
	Xucphr & Persuasion & 24\\
\end{DndTable}

"I'm still grieving over the loss of a family member" said Ruben as he tries to cry.
Dean Alistair notice that Ruben is very jumpy and pass his berievement process.
Ta'list complemented Dean Alistair's tophat and wanted to know more details on how to make hats.
Dean Alistair went on an in-depth conversation about top hats. 
Ta'lisk requested a private lesson on making the dimensional hat with the Dean in which he agreed.
Dean Allistair notice that Ruben's ability to summon his own familiar is impressive and left immediately to teach Ta'lisk

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Ruben & Investigation & 18\\
	Ruben & Perception & 20\\
	Ruben & Athletic & 20\\
	Brolasi & Investigation & 20\\
	Brolasi & Perception & 25\\
	Brolasi & Athletic & 16\\
\end{DndTable}

Ruben and Brolasi made it to Professor Lirienne Solvaine class to ask if she knew which class Yotash Nemonnis is currently located.
She did not know but directed the two adventurers to conjuration class held by Halveth Pell.
Ruben knew that he'll have to pass through Professor Kavel Dravaryn class, a retired War Mage with anger issues.

As they head towards Professor Pell's class, an explosion occurred within the classroom and a student started running away; it was Yotash Nemmonis.
Brolasi and Ruben instantly run after Yotash and followed him to the library. 
At the library, they caught him in in between the desks at the library.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Ruben & Strength & 19\\
	Ruben & Dexterity & 24\\
\end{DndTable}

Right as Ruben caught Yotash, he felt something going pass his head. Yotash shouted someone to stand down and admit that he is captured and in safe hands.
Suddenly, a small demon appeared next to Yotash; The demon's name is Kip.
Ruben said he wanted to catch up with Yotash but was ordered to send him to the Dean's office for the classroom explosion.
Kip and Ruben had an argument but Yotash said that Kip will "escort" him to the Dean's office and meet up at the courtyard by the potion class.
Kip explained that the contract he has with Yotash is "help with the development and growth of Yotash".
Ruben explained to Brolasi that killing Yip would cause an issue with the Nemmonis' family and sent a message to Pyretrix.
Pyretrix said to find out more details about the contract.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Ruben & Stealth & 21\\
	Brolasi & Stealth & 11\\
	Ruben & Stealth & 20\\
	Brolasi & Stealth & 20\\
\end{DndTable}

As Ruben and Brolai sneaking around they spotted Professor Kavel Daravaryn but were able to sneak pass him.
They sneak into the cafeteria and were inspired by the food there. Afterwards, they returned to the tavern.

\begin{DndSidebar}(Good Ass Food)
	Brolasi and Ruben gain inspiration from eating some bomb-ass food from the school.
\end{DndSidebar}

\section{Tavern}
\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Xucphr & Luck & 16\\
	Xucphr & Perception & 13\\
\end{DndTable}
Pyretrix and Xucphr saw Ruben, Brolasi, and Rayla return to the tavern.
Xucphr checked in on Ta'lisk and while they were discussing about top-hats, a small dragonborne and a demon walked into the Dean's office.
The Dean pause his lesson to talk to Yotash about what happened in class. Xucphr notice that Kip doesn't take his eyes off of Ta'lisk the entire time.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla & History & 11 (D)\\
\end{DndTable}
Pyretrix declared that The Sensational Seven need more information on the Nemmonis family.
Rayla suggest meeting Kavash but everyone decline the idea. Pyretrix wanted Rayla to use her friendship to gain information but Rayla refuse.
Suddenly a flash of memory came to Rayla; Kavash is actually a dick.
Kavash lied about helping kids on the street and made them fight over 1 gold piece.
Raya discuss this memory with the team and said drinking may make her remember what happened that night.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Rayla &Con & 25\\
	Xucphr &Con & 10\\
	Pryetrix &Con & 8\\
\end{DndTable}

Pyretrix and Xucphr blacked out while Rayla remembered everything that happened; She had a terrible time with Kavash.
Kavash talked about himself the whole time, let Raya pay for his prostitution, and stole a dress from a store to give to Rayla.
Rayla also spent Rayla's 500gp on the prostitute.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Ruben & Perception & 15\\
	Brolasi & Perception & 16\\
\end{DndTable}

Back at the school, Ruben and Brolasi see Yotash and Kip arguing about Yotash going to detention.
Yotash mention that Kip is his benefactor. Yotash explained that it's related to family business.
Yotash's mother is the only person he can trust when it comes to the family members.
Kip explained that he can be killed by normal means that would kill a devil; killing him in the hells or reciting his actual name.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Brolasi & Persuasion & 16\\
	Brolasi & Religion & 22\\
\end{DndTable}

Kip told Brolasi to try and kill him but Brolasi declined and campaign Monks for Punks.
Kip wanted Yotash to donate for their cause and Yotash donated 800gp to Brolasi.
As Kip talk, Brolasi know that if the devil that made the contract dies, from true death, all of their contracts becomes null and void.

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{Skill} & \textbf{d20} \\
	Brolasi & Perception & 23\\
	Ruben & Perception & 16\\
	Xucphr & Con Save & 21\\
\end{DndTable}

Before leaving, a student bump into Yotash and made him fall to the group. Kip transformed into a very large devil.
Yotash is trying to keep Kip calm. Kip calm down and shrunk in size.
Xucphr still see Ta'lisk talking to Dean Allistair about tophats for the past several hours.
Xucphr feel Ta'list brain straining from all the information about high-dimensional top hat; Blood comes out of Ta'lisk nose from the wealth of knowledge.
Dean Allistair notice that it's getting late and gave Ta'lisk his contact information for a later lesson.

\section{Tavern}
The Sensational Seven discuss about Ruben and Brolasi discussion with Kip and Yotash.
Pyretrix is upset due to the fact that Kip may be good and the team cannot kill him.
Out of anger, Pyretrix slept and dread that he will have to talk to Sid.

Xucphr explained that killing Kip may cause issues with the Nemmonis family while Sid may be a better choice to kill.
Xucphr also wanted to see if the team can trick Sid to attack Yotash for the devils to kill themselves.


\section*{Loot and Results}

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{item(s)} \\
	Rayla & 5 Potions (Remaining after sharing with the group)\\
	Ruben, Pyretrix, Brolasi, Xucphr, Nova & 2 potions (from Rayla) \\
	Ruben & Enhanced Gnome Weed (20 usage) \\
	Rayla & 10 Gold (Betting)\\
	Xucphr & 10 Gold (Betting)\\
	Brolasi & 100 Plat, 800 Gold, 2 Silver, 10 Copper\\

	Rayla & Sending Stone\\
	Xucphr & Amulet of Healing\\
	Xucphr & Frefil's Jolly Oozebean Sugarbombs\\

\end{DndTable}

\section*{End of Session 11}
