\chapter*{Journey to Thalvarien}
\section{Tavern}

\DndDropCapLine{B}{efore turning in for the night} Xucphr, Pyretrix,
and Ruben discussed what’s the next step for
handling their current situation. Brolasi said
that we can try again tomorrow since Ruben and
them talk to Kip and Yotash already today.

Xucphr decided to talk to the bartender, who
later introduce themselves as Bob, to get some
info on Kavash and Kip. The bartender mention
that someone in our party knows about Kavash
but never said who. As Pyretrix and Brolasi turn
in for the night, Rayla wonder around town while
Ruben went to see Namash Drephac. Namash
said he could not crfted the weapon for Ruben
but provided Ruben with a Blunderbuss and
new skateboard. Afterwards, Ruben head back
to the cavern.

\section{Toy Shop}
Rayla wonder around town and found a toy shop.
Xucphr also found the toy shop from strolling
around town. Xucphr peformed the ritual for
Identify within the toyshop. Shopkeeper kicked
Xucphr and Rayla out and banned Xucphr for
scaring the childern.

\section{The Bejeweled Tits}
Rayla goes back to the club to meet Kavash.
Xucphr summon Ta’lisk to follow Rayla; Ta’lisk
turn invisible following Rayla. Ruben and
Pyretrix heard scuffling noise outside the Tavern.
Ruben and Pyretrix followed the noise. Ruben
and Pyretrix see Xucphr outside of the club and
all three went inside stealth-like.

Kavash wanted everyone to drink the very
potent liquor that made Xucphr drunk and
Rayla pass out. Kavash brough out some powder
and preoceed to snort the shit out of the powder;
Kavash is very high right now. Kavash sprayed
the powder towards Pyretrix and Pyretrix became
high. Everyone else was able to avoid the
powder.

Ruben was the only person in the room not
drunk or high. Kavash talked to Ruben about
joining his quest to kill Kip. Ruben denied the
group’s attempt to assassinate Kip but Kavash
revealed that the bartender is working for him
and knows where the group stays. After getting
really high, Kavash attempted to grab Rayla and
Xucphr in an attempt to leave the club; Kavash
just wanted to murder someone. Ruben
contained Kavash with an Entanglement spell
and Xucphr calm Kavash with a Suggestion
spell.

After Kavash pulled out a bong and start
smoking, Kavash revealed that he talked to the
older brother about killing Kip. The older
brother, Bragos, wasn’t happy and tormented
Kavash and beat him (keeping the details PG13).
Kavash snuck into Kip and Yotash’s dormatory,
banished Kip to hell, and beat the shit out of
Yotash.

Kavash also mention that this happend 3
hours ago, Kip should be back from the
banishment, and left a note in the room. The
note said "The Bubble Buddies sends their
reguards!"

Pyretrix and Rayla, from Kavash’s description,
know that Kip is a Pit fiend and would be a
rough fight for the team.



\section*{Loot and Results}

\begin{DndTable}[color=PhbLightCyan]{cXX}
	\textbf{Character} & \textbf{item(s)} \\
	Rayla & 5 Potions (Remaining after sharing with the group)\\
	Ruben, Pyretrix, Brolasi, Xucphr, Nova & 2 potions (from Rayla) \\
	Ruben & Enhanced Gnome Weed (20 usage) \\
	Rayla & 10 Gold (Betting)\\
	Xucphr & 10 Gold (Betting)\\
	Brolasi & 100 Plat, 800 Gold, 2 Silver, 10 Copper\\

	Rayla & Sending Stone\\
	Xucphr & Amulet of Healing\\
	Xucphr & Frefil's Jolly Oozebean Sugarbombs\\

\end{DndTable}

\section*{End of Session 11}
