\chapter*{Xucphr}

\section{Xucphr}

\subsection {Cantrips}
\DndSpellHeader%
  {\textbf{Eldritch Blast}}
  {Evocation Cantrip}
  {1 action}
  {120 feet}
  {V, S}
  {Instantaneous}
  %{\textbf{Attack/Save}: WIS 13}\\\
  
You hurl a beam of crackling energy. Make a ranged spell attack against one creature or object in range. On a hit, the target takes 1d10 Force damage.

{\textbf{Cantrip Upgrade.}}  The spell creates two beams at level 5, three beams at level 11, and four beams at level 17. You can direct the beams at the same target or at different ones. Make a separate attack roll for each beam.


\DndSpellHeader%
{\textbf{Mage Hand}}
{Conjuraction Cantrip}
{1 action}
{30 ft.}
{V, S}
{1 minute}
%{\textbf{Attack/Save}: WIS 13}\\\

A spectral, floating hand appears at a point you choose within range. The hand lasts for the duration. The hand vanishes if it is ever more than 30 feet away from you or if you cast this spell again.

When you cast the spell, you can use the hand to manipulate an object, open an unlocked door or container, stow or retrieve an item from an open container, or pour the contents out of a vial.

As a Magic action on your later turns, you can control the hand thus again. As part of that action, you can move the hand up to 30 feet.

The hand can’t attack, activate magic items, or carry more than 10 pounds.


\DndSpellHeader%
{\textbf{Magic Stone}}
{Transmutation Cantrip}
{1 bonus action}
{Touch}
{V, S}
{1 minute}
%{\textbf{Attack/Save}: WIS 13}\\\

You touch one to three pebbles and imbue them with magic. You or someone else can make a ranged spell attack with one of the pebbles by throwing it or hurling it with a sling. If thrown, it has a range of 60 feet. If someone else attacks with the pebble, that attacker adds your spellcasting ability modifier, not the attacker’s, to the attack roll. On a hit, the target takes bludgeoning damage equal to 1d6 + your spellcasting ability modifier. Hit or miss, the spell then ends on the stone.

If you cast this spell again, the spell ends early on any pebbles still affected by it.



\DndSpellHeader%
{\textbf{Mending}}
{Transmutation Cantrip}
{At Will}
{Touch}
{V, S,M (two lodestones)}
{1 minute}
%{\textbf{Attack/Save}: WIS 14}\\\

This spell repairs a single break or tear in an object you touch, such as a broken chain link, two halves of a broken key, a torn cloak, or a leaking wineskin. As long as the break or tear is no larger than 1 foot in any dimension, you mend it, leaving no trace of the former damage.

This spell can physically repair a magic item or construct, but the spell can't restore magic to such an object.

\DndSpellHeader%
{\textbf{Moment to Think}}
{Transmutation Cantrip}
{1 bonus action}
{Self}
{V}
{Instantaneous}
%{\textbf{Attack/Save}: WIS 14}\\\

When you cast this spell, you briefly stop time for everyone but yourself. You can take one additional action and move around in your space while no time passes for other creatures. That action can be used only to take the Search, Study, or Utilize action. Furthermore, you can’t affect or damage any creature or object, other than objects you are wearing or carrying. If an object leaves your hand, it also becomes frozen in time.


\DndSpellHeader%
{\textbf{Prestidigitation}}
{Transmutation Cantrip}
{1 action}
{10 ft}
{V,S}
{1 hour}
%{\textbf{Attack/Save}: WIS 14}\\\

You create a magical effect within range. Choose the effect from the options below. If you cast this spell multiple times, you can have up to three of its non-instantaneous effects active at a time.

{\textbf{Sensory Effect.}} You create an instantaneous, harmless sensory effect, such as a shower of sparks, a puff of wind, faint musical notes, or an odd odor.

{\textbf{Fire Play.}} You instantaneously light or snuff out a candle, a torch, or a small campfire.

{\textbf{Clean or Soil.}} You instantaneously clean or soil an object no larger than 1 cubic foot.

{\textbf{Minor Sensation.}} You chill, warm, or flavor up to 1 cubic foot of nonliving material for 1 hour.

{\textbf{Magic Mark.}} You make a color, a small mark, or a symbol appear on an object or a surface for 1 hour.

{\textbf{Minor Creation.}} You create a nonmagical trinket or an illusory image that can fit in your hand. It lasts until the end of your next turn. A trinket can deal no damage and has no monetary worth.



\subsection {Class Features}
\begingroup
\DndSetThemeColor[PhbMauve]
\begin{DndComment}{Eldritch Invocations}
	You have unearthed Eldritch Invocations, pieces of forbidden knowledge that imbue you with an abiding magical ability or other lessons. If an invocation has a prerequisite, you must meet it to learn that invocation.
	
	{\textbf{Repelling Blast}}
	Choose one of your known Warlock cantrips that requires an attack roll. When you hit a Large or smaller creature with that cantrip, you can push the creature up to 10 ft. straight away from you.
	
	{\textbf{Eldritch Spear}}
	Choose one of your known Warlock cantrips that deals damage and has a range of 10+ feet. When you cast that spell, its range increases by {\textbf{210 ft.}}
	
	You can also expend 5 Hit Points from the pool of healing power to remove the Poisoned condition from the creature; those points don’t also restore Hit Points to the creature.
	
	{\textbf{Pact of the Tome}}
	At the end of a Short or Long Rest you can conjure forth a book in your hand, a Book of Shadows, which contains eldritch magic that only you can access, granting the benefits below.
	
	• When the book appears, choose 3 cantrips and choose two level 1 spells that have the Ritual tag, which can be from any class’s spell list.
	
	• You can use the book as a Spellcasting Focus.
	
	The book disappears if you conjure another one or if you die.
	
	{\textbf{Agonizing Blast (Eldritch Blast)}}
	You can add your Cha. modifier bonus to the damage rolls of Eldritch Blast.
	
	{\textbf{Eldritch Mind}}
	You have Advantage on Con. saving throws that you make to maintain Concentration.
	
	{\textbf{Pact of the Chain}}
	You learn Find Familiar and can cast it as a Magic action without expending a spell slot.
	
	When you take the Attack action, you can forgo one of your own attacks to allow your familiar to make one attack with its Reaction
	
	
\end{DndComment}

\begin{DndComment}{Eldritch Heads}
	You gain 3 eldritch heads. Only you and creatures with truesight can see these heads, which sprout from your shoulders as representations of your patron. You can choose to ignore the heads and cause them to vanish from your vision. These eldritch heads grant you the following benefits:
	
	Once per turn, you can expend one head when you hit a creature with an attack to cause that creature to take extra 4 psychic damage.
	
	When you make a Charisma (Intimidation) check, you can expend one head to gain advantage on the roll. When you do, your eldritch heads become briefly visible to everyone.
	
	When you fail a death saving throw, you can expend one head to succeed instead.
	
	You regain all expended heads when you finish a long rest. In addition, you can use a bonus action to beseech your patron to restore two of your expended heads. Once you use this ability, you can’t use it again until you finish a long rest.
	
\end{DndComment}





\endgroup

