\chapter*{}

\section{Ruben}

\subsection {Attack}
\DndSpellHeader%
  {\textbf{Canseco Bat}}
  {Warhammer}
  {1 action}
  {5 feet}
  {Versatile (1d10), Push}
  {Instantaneous}
  %{\textbf{Attack/Save}: WIS 13}\\\
his baseball bat uses the statistics of a +1 warhammer. 
If a hostile creature misses you with a ranged spell attack while wielding this bat, you can use your reaction to redirect the attack at another creature you can see within 30 feet of you, using this weapon’s attack bonus for the new attack roll. 
Once you use this property, you can’t do so again until the next dawn.


\subsection {Cantrips}
\DndSpellHeader%
  {\textbf{Toll the Dead}}
  {Necromancy Cantrip}
  {1 action}
  {60 feet}
  {V, S}
  {Instantaneous}
  %{\textbf{Attack/Save}: WIS 13}\\\
  
You point at one creature you can see within range, and the sound of a dolorous bell fills the air around it for a moment. The target must succeed on a Wisdom saving throw or take 1d8 necrotic damage. If the target is missing any of its hit points, it instead takes (1d12) necrotic damage.

{\textbf{Cantrip Upgrade.}} The spell’s damage increases by one die when you reach 5th level (2d8 or 2d12), 11th level (3d8 or 3d12), and 17th level (4d8 or 4d12).


\DndSpellHeader%
{\textbf{Vengeful Blade}}
{Evocation Cantrip}
{1 action}
{Self}
{S, M (a melee weapon worth at least 1 gp)}
{Instantaneous}
%{\textbf{Attack/Save}: WIS 13}\\\

You brandish the weapon used in the spell’s casting and make a melee attack with it against one creature within 5 feet of you. On a hit, the target suffers the weapon attack’s normal effects and then radiates a dark aura of energy until the start of your next turn. If the target makes an attack or casts a spell before then, the target takes (1d8) necrotic damage and the spell ends.

\textbf{Cantrip Upgrade.} This spell’s damage increases when you reach certain levels. At 5th level, the melee attack deals an extra 1d8 necrotic damage to the target on a hit, and the damage the target takes for making an attack or casting a spell increases to 2d8. Both damage rolls increase by 1d8 at 11th level (2d8 and 3d8) and again at 17th level (3d8 and 4d8).


\subsection {Class Features}
\begingroup
\DndSetThemeColor[PhbMauve]

\begin{DndComment}{Fighting Style}
	You have honed your martial prowess and gain a Fighting Style feat of your choice.
	Whenever you gain a Fighter level, you can replace the feat you chose with a different Fighting Style feat.
\end{DndComment}


\begin{DndComment}{Second Wind}
	As a Bonus Action, you can draw upon a limited well of physical and mental stamina and regain {1d10+7} HP. 
	You can use this 3 times per Long Rest, and can regain one expended use when you finish a Short Rest.
\end{DndComment}

\begin{DndComment}{Action Surge}
	You can push yourself beyond your normal limits for a moment. On your turn, you can take one additional action, except the Magic action.
	Once you use this feature, you can’t do so again until you finish a Short or Long Rest. 
	Starting at level 17, you can use it twice before a rest but only once on a turn.
\end{DndComment}

\begin{DndComment}{Weapon Mastery}
	Your training with weapons allows you to use the mastery properties of three kinds of Simple or Martial weapons of your choice. 
	Whenever you finish a Long Rest, you can practice weapon drills and change one of those weapon choices.
	
	When you reach certain Fighter levels, you gain the ability to use the mastery properties of more kinds of weapons, as shown in the Weapon Mastery column of the Fighter Features table.
	
	\textbf{Warhammer (Push):} Your training with weapons allows you to use the mastery property of Warhammers:
	\textbf{Push:} If you hit a creature with Warhammer, you can push the creature up to 10 feet straight away from yourself if it is Large or smaller.

	\textbf{Quarterstaff (Topple):} Your training with weapons allows you to use the mastery property of Quarterstaffs:
	
	\textbf{Topple:} If you hit a creature with a Quarterstaff, you can force the creature to make a Constitution saving throw (DC 8 plus the ability modifier used to make the attack roll and your Proficiency Bonus). On a failed save, the creature has the Prone condition.
	
	\textbf{Club (Slow):} Your training with weapons allows you to use the mastery property of Clubs:
	
	\textbf{Slow:}  If you hit a creature with a Club and deal damage to it, you can reduce its Speed by 10 feet until the start of your next turn. 
	If the creature is hit more than once by weapons that have this property, the Speed reduction doesn’t exceed 10 feet.
	
	\textbf{Topple (Quarterstaff):} 1 Action
	\textbf{Push (Warhammer):} 1 Action
	\textbf{Slow (Club):} 1 Action

\end{DndComment}


\begin{DndComment}{Tactical Mind}
	You have a mind for tactics on and off the battlefield. 
	When you fail an ability check, you can expend a use of your Second Wind to push yourself toward success. 
	Rather than regaining Hit Points, you roll 1d10 and add the number rolled to the ability check, potentially turning it into a success. 
	If the check still fails, this use of Second Wind isn’t expended.
	
\end{DndComment}

\begin{DndComment}{Giant's Might}
	You have learned how to imbue yourself with the might of giants. As a bonus action, you magically gain the following benefits, which last for 1 minute:

	If you are smaller than Large, you become Large, along with anything you are wearing. If you lack the room to become Large, your size doesn’t change.
	You have advantage on Strength checks and Strength saving throws.
	Once on each of your turns, one of your attacks with a weapon or an unarmed strike can deal an extra 1d6 damage to a target on a hit.
	You can use this feature a number of times equal to your proficiency bonus, and you regain all expended uses of it when you finish a long rest.
\end{DndComment}


\endgroup

