\chapter*{}

\section{Pyretrix}

\subsection {Attack}
\DndSpellHeader%
  {\textbf{Greataxe +1}}
  {Weapon}
  {1 action}
  {5 feet}
  {Slashing (1d12+5)}
  {Instantaneous}
  %{\textbf{Attack/Save}: WIS 13}\\\
You have a +1 bonus to attack and damage rolls made with this magic weapon.

\textbf{Cleave.} If you hit a creature with a melee attack roll using a Greataxe, you can make a melee attack roll with the Greataxe against a second creature within 5 feet of the first that is also within your reach. 
On a hit, the second creature takes the Greataxe’s damage, but don’t add your ability modifier to that damage unless that modifier is negative. 
You can make this extra attack only once per turn.

\DndSpellHeader%
  {\textbf{Handaxe}}
  {Weapon}
  {1 action}
  {5 feet/ 20ft - 60ft (thrown)}
  {Slashing (1d12+4)(2d6 Fire)(3d6 Lightning - during Fissi)}
  {Instantaneous}
  %{\textbf{Attack/Save}: WIS 13}\\\
Proficiency with a Handaxe allows you to add your proficiency bonus to the attack roll for any attack you make with it.

\textbf{Vex.} If you hit a creature with a Handaxe and deal damage to the creature, you have Advantage on your next attack roll against that creature before the end of your next turn.


\DndSpellHeader%
  {\textbf{Starmetal Solar Axe (Greataxe)}}
  {Weapon}
  {1 action}
  {5 feet}
  {Slashing (1d12+5)}
  {Instantaneous}
  %{\textbf{Attack/Save}: WIS 13}\\\
This magic weapon is forged using iron from the stars. 
While you’re attuned to this weapon, you can call upon its latent stellar energy to catalyze change within the metal, creating endothermic and exothermic reactions.
The weapon can be fissioned into two separated Battleaxes or fused back into a Greataxe. 
It has the following properties based on its current state:

\textbf{Fused State (Greataxe).} You gain a +1 bonus to attack rolls and damage rolls made with this magic weapon, which deals an extra 2d6 Fire damage on a hit.
While holding the axe, flames erupt from its edges and a small star burns in its center. 
These flames shed Bright Light in a 20-foot radius and Dim Light for an additional 20 feet. The light is sunlight.

\textbf{State Change.}This weapon can change between its two states using the following properties:

\textbf{Fission.} While holding the fused Greataxe, you can take a Bonus Action and use a command word to magically split it apart into its fissioned state. 
When you do, electrical energy is released, forcing other creatures within 30 feet of you to make a DC 17 Dexterity saving throw. 
A creature takes 3d6 Lightning damage on a failed save or half as much damage on a successful one. 
This property can’t be used again for 12 hours.

Your training with weapons allows you to use the mastery property of Greataxes:

\textbf{Cleave.} If you hit a creature with a melee attack roll using a Greataxe, you can make a melee attack roll with the Greataxe against a second creature within 5 feet of the first that is also within your reach. 
On a hit, the second creature takes the Greataxe’s damage, but don’t add your ability modifier to that damage unless that modifier is negative. 
You can make this extra attack only once per turn.

\DndSpellHeader%
  {\textbf{Breath Weapon (Fire)}}
  {Breath Weapon}
  {1 action}
  {15ft Cone or 30ft Line/5ft wide}
  {2d10 (Fire)}
  {Instantaneous}
  {\textbf{Attack/Save}: DEX 14}\\\
When you take the Attack action on your turn, you can replace one of your attacks with an exhalation of magical energy in either a 15-foot Cone or a 30-foot Line that is 5 feet wide (choose the shape each time).
Each creature in that area must make a Dexterity saving throw (DC 8 plus your Constitution modifier and Proficiency Bonus).
On a failed save, a creature takes 1d10 Fire damage. On a successful save, a creature takes half as much damage. 
This damage increases by 1d10 when you reach character levels 5 (2d10), 11 (3d10), and 17 (4d10).

You can use this Breath Weapon a number of times equal to your Proficiency Bonus, and you regain all expended uses when you finish a Long Rest.


\subsection {Class Features}
\begingroup
\DndSetThemeColor[PhbMauve]

\begin{DndComment}{Fighting Style}
	You have honed your martial prowess and gain a Fighting Style feat of your choice.
	Whenever you gain a Fighter level, you can replace the feat you chose with a different Fighting Style feat.
\end{DndComment}


\begin{DndComment}{Second Wind}
	As a Bonus Action, you can draw upon a limited well of physical and mental stamina and regain {1d10+7} HP. 
	You can use this 3 times per Long Rest, and can regain one expended use when you finish a Short Rest.
\end{DndComment}

\begin{DndComment}{Action Surge}
	You can push yourself beyond your normal limits for a moment. On your turn, you can take one additional action, except the Magic action.
	Once you use this feature, you can’t do so again until you finish a Short or Long Rest. 
	Starting at level 17, you can use it twice before a rest but only once on a turn.
\end{DndComment}

\begin{DndComment}{Weapon Mastery}
	Your training with weapons allows you to use the mastery properties of three kinds of Simple or Martial weapons of your choice. 
	Whenever you finish a Long Rest, you can practice weapon drills and change one of those weapon choices.
	
	When you reach certain Fighter levels, you gain the ability to use the mastery properties of more kinds of weapons, as shown in the Weapon Mastery column of the Fighter Features table.
	
	\textbf{Warhammer (Push):} Your training with weapons allows you to use the mastery property of Warhammers:
	\textbf{Push:} If you hit a creature with Warhammer, you can push the creature up to 10 feet straight away from yourself if it is Large or smaller.

	\textbf{Quarterstaff (Topple):} Your training with weapons allows you to use the mastery property of Quarterstaffs:
	
	\textbf{Topple:} If you hit a creature with a Quarterstaff, you can force the creature to make a Constitution saving throw (DC 8 plus the ability modifier used to make the attack roll and your Proficiency Bonus). On a failed save, the creature has the Prone condition.
	
	\textbf{Club (Slow):} Your training with weapons allows you to use the mastery property of Clubs:
	
	\textbf{Slow:}  If you hit a creature with a Club and deal damage to it, you can reduce its Speed by 10 feet until the start of your next turn. 
	If the creature is hit more than once by weapons that have this property, the Speed reduction doesn’t exceed 10 feet.
	
	\textbf{Topple (Quarterstaff):} 1 Action
	\textbf{Push (Warhammer):} 1 Action
	\textbf{Slow (Club):} 1 Action

\end{DndComment}


\begin{DndComment}{Tactical Mind}
	You have a mind for tactics on and off the battlefield. 
	When you fail an ability check, you can expend a use of your Second Wind to push yourself toward success. 
	Rather than regaining Hit Points, you roll 1d10 and add the number rolled to the ability check, potentially turning it into a success. 
	If the check still fails, this use of Second Wind isn’t expended.
	
\end{DndComment}

\begin{DndComment}{Giant's Might}
	You have learned how to imbue yourself with the might of giants. As a bonus action, you magically gain the following benefits, which last for 1 minute:

	If you are smaller than Large, you become Large, along with anything you are wearing. If you lack the room to become Large, your size doesn’t change.
	You have advantage on Strength checks and Strength saving throws.
	Once on each of your turns, one of your attacks with a weapon or an unarmed strike can deal an extra 1d6 damage to a target on a hit.
	You can use this feature a number of times equal to your proficiency bonus, and you regain all expended uses of it when you finish a long rest.
\end{DndComment}


\endgroup

