\DndArea{Noctheria}

\DndSubArea{Border of Noctheria}
When crossing the border, the group notice it's suddenly nighttime. When crossing back, it is suddenly daytime.

\DndSubArea{Forrest}
	Heavy forest area around the village. Several bushes and grass-areas rustling as if there's something moving around, watching the village. The Sensational Seven were warned about "The Feral One" in the forest. A feral roar came from the forest and the horrifying sound agitated Axe Beaks.
	
\DndSubArea{Village}
The village looks like complete and utter shit. The houses look unkept and broken down. The adventures are told the villagers are on a strictly vegetarian diet (that's bullshit but I believe it). Two trails lead towards the Matriarch of the land. One trail lead towards the forest and another takes you through a long path through the mountains.

%\DndSubArea{Building A}
%The adventurers asked for directions from the man inside the building and directed them to go to Vladmir's Keep

\DndArea{House of Orlovski}
	A masquerade ball is held at the Orlovski's estate; only one guest per house were invited. Guests are handed a masquerade mask that \textbf{must} stay on inside the house but can be taken off once outside.
	
\DndSubArea{Ballroom}
	Bards at the end of the hall playing fancy music; Classical music. Candles and lights all around. Servants appear to be frail and weak; darkness and gloom around their eyes. Guests are seen discussing political topics such as economics, eating a banquet of food all around the outside of the ballroom, and dancing with grace and class.
	
%2025-12-1 This lore is for Kor Volar
\begin{DndSidebar}[float=!b]{Kor Volar}
A militarized republic, led by a council of general. The capital, Stonecradle, is a  mountain fortress and cannon foundry. Noctheria is in the mountains East of Tellus with a few ports and trades. It is known for flintlock militias, black steelworks, and their tactical engineering schools. The people here prefer isolation and solitude. Currently House Morvane campaigns for war with the southern nations to secure new lands.
%	Daytime is 4 hours and nighttime is 20 hours.
\end{DndSidebar}