\DndArea{Noctheria}

\DndSubArea{Border of Noctheria}
When crossing the border, the group notice it's suddently nighttime. When crossing back, it is suddenly daytime.

\DndSubArea{Forrest}
	Heavy forest area around the village. Several bushes and grass-areas rustling as if there's something moving around, watching the village. The Sensational Seven were warned about "The Fereal One" in the forest. A fereal roar came from the forest and the horrifying sound aggitated Axe Beaks.
	
\DndSubArea{Village}
The village looks like complete and utter shit. The houses look unkept and broken down. The adventures are told the villagers are on a strickly vegetaria diet (that's bullshit but I believe it). Two trails lead towards the Matriarch of the land. One trail lead towards the forest and another takes you through a long path through the mountains.

%\DndSubArea{Building A}
%The adventurers asked for directions from the man inside the building and directed them to go to Vladmir's Keep

\DndArea{House of Orlovski}
	A masquerade ball is held at the Orlovski's estate; only one guest per house were invited. Guests are handed a masquerade mask that \textbf{must} stay on inside the house but can be taken off once outside.
	
\DndSubArea{Ballroom}
	Bards at the end of the hall playing fancy music; Classical music. Candles and lights all around. Servants appear to be frail and weak; darkness and gloom around their eyes. Guests are seen discussing political topics such as economics, eating a banquest of food all around the outside of the ballroom, and dancing with grace and class.
	
\begin{DndSidebar}[float=!b]{Noctheria, "\textit{While the Sun Dies, We Endure}"}

	A matriarchy supported by Matriarchal Houses where the capital, Vathmir Keep, is often called "\textit{The Heart That Bleeds}".Noctheria is known for exports of alchemical reagents, blacksteel, silks, artwork, and luxury wines. The villagers are not known for a social life and prefer total isolation. Currently, House Morvane campaigns for war with the southern nations to secure new land. Daytime is 4 hours and nighttime is 20 hours.
\end{DndSidebar}