\DndArea{Border of Thalvarien}
Forrest area with a small town consisting of 5 buildings; two houses, a general store, a potion shop, and a tavern.
\DndSubArea{Forrest}
	Heavy forest area around the village. 
\DndSubArea{Potion Shop}
	A mushroom-shaped building that is owned by a minitaur named Sebastian Steer.

\DndArea{Thalvarien}
	Very large city state with a giant wall that surround the area.
	Town is a pyramid-like shape with building made of white marble and smell of gunpowder.
	Paved roads everywhere, which is not common for most towns, with sidewalks and a small amount of steam machines.


\DndSubArea{The Dragon's Hoarde}
	A well known jewerly store in Thalvarian.
	A halfling is the owner of the establishment with a few employees.
\DndSubArea{The One-Eyed Beholder}
	A tavern where the owner/bartender is a One-eyed Beholder.
	When the bar close, the bartender tend to lay on the ground with their eyes open; mimic other creatures sleeping
	A snapping turtle stand outside the bar entrance; a bouncer who has a zero-tolerance for violence.

\DndSubArea{Th Bejeweled Tits}
	A popular, large night club that welcome all patrons.
	Smoke, lights, and magic beams (laser-effect) created by several wizards.
	Large stage area for performers, musicians, etc. followed by large floating platforms next to the stage.

\begin{DndSidebar}[float=!b]{Thalvarien Noble Families}
	\begin{itemize}
		\item[*]Blackcrest: Head Family of the Gunpowder Guild
		\item[*]Nemmonis: Head Mercantile Guild and Financial Advisor to House Valcorin
		\item[*]Zyndar: Drow Noble House and Founder of Arcantine College in Caelbaris
		\item[*]Vecona: One of the oldest families in Thalvarien and main contributor of donations to the Arcantine College. Long bloodline of Arcantine Alumni.
		\item[*]Caelbre: Founding family of the capital of Thalvarien, original ruling family.
	\end{itemize}
\end{DndSidebar}
%2025-12-1 This lore is for Kor Volar
%\begin{DndSidebar}[float=!b]{Kor Volar}
%A constational monarchy with a powerful merchant nobility. The capital, Caelbaris, is know as a shining city built on marble cliffs. Thalvarien is know for gunpowder, manufacturing, power naval strength, and artificer guilds. House words: "Progress, above all".
%\end{DndSidebar}